DeepPicar: A Low-cost Deep Neural Network-based Autonomous Car

### 2018-04-20 paper/evaluation-drampart.tex
..

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{figs/memguard_multicore}
  \caption{ Memory bandwidth sensitivity of the control loop 
execution time. }
  \label{fig:memguard_multicore}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{figs/memguard_bandwidth}
  \caption{Timing impact of co-scheduling memory intensive
co-runners when memory bandwidth throttling is enabled. }
  \label{fig:memguard_bandwidth}
\end{figure}

>>>>

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{figs/memguard_multicore}
  \caption{Memory bandwidth sensitivity of the CNN control loop.}
  \label{fig:memguard_multicore}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{figs/memguard_bandwidth}
  \caption{Effect of throttling three memory intensive co-runners.} 
  \label{fig:memguard_bandwidth}
\end{figure}
